\item [3.7] Consider the linear algebraic equation

\begin{equation*}
 \begin{bmatrix}
  2 & -1\\
  -3 & 3\\
  -1 & 2
 \end{bmatrix}
\mathbf{x} =
\begin{bmatrix}
 1\\
 0\\
 1
\end{bmatrix}
= \mathbf{y}
\end{equation*}

It has three equations and two unkowns.
Does a solution $\mathbf{x}$ exist in the equations?
Is the solution unique?
Does a solution exist if $\mathbf{y} = [1 1 1]'$?\\

Yes, there is a solution to the system of equations. It is
an \emph{unique} solution.
This is due to the fact that the
second row of the expanded matrix is a linear combination of
the other two rows of the matrix.
In other words, the rank of the matrix matches
the number of unkowns ($\rho(\mathbf{A}) = 2$).
\\

\begin{align*}
  \begin{bmatrix}
    2 & -1\\ -3 & 3\\-1 & 2
  \end{bmatrix}
  \begin{bmatrix}
   x_1 \\x_2
  \end{bmatrix}
    & =
    \begin{bmatrix}1\\  0\\  1\end{bmatrix}\\
    \begin{bmatrix}
    2 x_1 - x_2\\ -3 x_1 + 3 x_2\\-x_1 + 2 x_2
  \end{bmatrix} &= \begin{bmatrix}1\\  0\\  1\end{bmatrix}\\
  -3 x_1 + 3 x_2 = 0 & \rightarrow x_1 = x_2\\
  2 x_1 - x_2 = 1 & \rightarrow x_1 = 1 \rightarrow x_2 = 1\\
  - x_1 + 2 x_2 = 1 & \rightarrow x_2 = 1
\end{align*}

There is no contradiction in the system of equations.



For $\mathbf{y} = [1 \; 1 \; 1]'$ there is no solution to the system of
equations.
The second row is no longer a linear
combination of the other two.
When solving the system
of equations we arrive at a contradiction.


\begin{align*}
  \begin{bmatrix}
    2 & -1\\ -3 & 3\\-1 & 2
  \end{bmatrix}
  \begin{bmatrix}
   x_1 \\x_2
  \end{bmatrix}
    & =
    \begin{bmatrix}1\\  1\\  1\end{bmatrix}\\
    \begin{bmatrix}
    2 x_1 - x_2\\ -3 x_1 + 3 x_2\\-x_1 + 2 x_2
  \end{bmatrix} &= \begin{bmatrix}1\\  1\\  1\end{bmatrix}\\
  -3 x_1 + 3 x_2 = 1 & \rightarrow x_1 = x_2 -\frac{1}{3}\\
  2 x_1 - x_2 = 1 & \rightarrow x_2 = \frac{5}{3} \rightarrow x_1 = \frac{4}{3}\\
  \text{But} & \\
  - x_1 + 2 x_2 = 1 & = - \frac{4}{3} + 2 (\frac{5}{3}) = 2 \neq 1
\end{align*}

We have arrived at a contradiction, thus the system has no solution.
